An event-sourced and distributed database with IPLD and materialized views

### 2019-09-19 draft.tex
lots of figure layout changes; added "examples" type
Signed-off-by: andrew <andrew@textile.io>

@@

\begin{figure}
  \includegraphics[width=\linewidth]{boat.jpg}
  \caption{The crypographic hash of content is used to make a request to the network of IPFS peers. Using the built-in routing machanisms and the distributed hash table, a peer(s) hosting the requested content is identified and content is returned. }
  \label{fig:contentaddressing}
\end{figure}

@@

@@

\begin{figure*}
\centering
\begin{minipage}{0.6\textwidth}
\begin{lstlisting}
// Log multiaddress
ipel := "/ipel/12D3KooWC2zyCVron7AA34N6oKNtaXaZB51feG9rBkr7QbCcW8ab"

// Address book
[
  "/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab",
  "/p2p/12D..dJT6nXY/ipel/12D..bCcW8ab" // Follower
]
\end{lstlisting}
\end{minipage}
  \caption{The Log Multiaddress.}
  \label{fig:boat1}
\end{figure*}

Much like IPFS Peers, Logs are identified on the network with addresses, or more specifically, with multiaddresses [ref]. Here we introduce IPEL, or Interplanetary Event Log, as a new protocol tag to be used when composing Log multiaddresses:\\

In practice, to reach a Log via it’s IPEL multiaddress, it must be encapsulated in an IPFS Peer multiaddress:

@@

\begin{minipage}{.45\textwidth}
\begin{lstlisting}
// AddrBook stores log addresses
type AddrBook interface {
   AddAddr(thread.ID, peer.ID, ma.Multiaddr, time.Duration)
   AddAddrs(thread.ID, peer.ID, []ma.Multiaddr, time.Duration)
   SetAddr(thread.ID, peer.ID, ma.Multiaddr, time.Duration)
   SetAddrs(thread.ID, peer.ID, []ma.Multiaddr, time.Duration)
   UpdateAddrs(t thread.ID, id peer.ID, oldTTL time.Duration, newTTL time.Duration)
   Addrs(thread.ID, peer.ID) []ma.Multiaddr
   ClearAddrs(thread.ID, peer.ID)
}
\end{lstlisting}
\end{minipage}

@@

@@

Much like the Log address book, Log keys are stored in a key book:

\begin{minipage}{.45\textwidth}
\begin{lstlisting}
// KeyBook stores log keys
type KeyBook interface {
   PubKey(thread.ID, peer.ID) ic.PubKey
   AddPubKey(thread.ID, peer.ID, ic.PubKey) error
   PrivKey(thread.ID, peer.ID) ic.PrivKey
   AddPrivKey(thread.ID, peer.ID, ic.PrivKey) error
   ReadKey(thread.ID, peer.ID) []byte
   AddReadKey(thread.ID, peer.ID, []byte) error
   FollowKey(thread.ID, peer.ID) []byte
   AddFollowKey(thread.ID, peer.ID, []byte) error
}
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{.45\textwidth}
\begin{lstlisting}
type TextileKVStore interface {
  Put(key string, value interface{}) error
  Get(key string) (interface{}, error)
  Del(key string) error
}
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{.45\textwidth}
\begin{lstlisting}
type TextileDocumentStore interface {
  Put(doc Inedexable) error
  Get(key string) (Indexable, error)
  Del(key string) error
  Query(query Query) ([]Indexable, error)
}
\end{lstlisting}
\end{minipage}

@@

\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=json,firstnumber=1]
{
  "_id": "bafykrq5i25vd64ghamtgus6lue74k", // TID
  "default": "no-access",
  "peers": {
    "12D..dwaA6Qe": ["write", "delete"],
    "12D..dJT6nXY": ["follow"],
    "12D..P2c6ifo": ["read"],
  }
}
\end{lstlisting}
\end{minipage}

@@

\begin{lstlisting}[language=json,firstnumber=1]
{
  "_id": "bafykrq5i25vd64ghamtgus6lue74k-acl", // TID-acl
  "default": "no-access",
  "peers": {
    "12D..dwaA6Qe": ["write", "delete"],
  }
}
\end{lstlisting}

@@

\begin{figure*}

@@

\end{figure*}

>>>>

\usepackage{trivfloat}
\trivfloat{example}

@@

\begin{figure}
  \includegraphics[width=\linewidth]{figures/Hash_Request.png}
  \caption{The crypographic hash of content is used to make a request to the network of IPFS peers. Using the built-in routing machanisms and the distributed hash table, a peer(s) hosting the requested content is identified and content is returned. }
  \label{fig:contentaddressing}
\end{figure}

@@

\begin{example*}
\centering
\begin{minipage}{0.7\textwidth}
\begin{lstlisting}
// Log multiaddress
ipel := "/ipel/12D3KooWC2zyCVron7AA34N6oKNtaXaZB51feG9rBkr7QbCcW8ab"

// Address book
[
  "/p2p/12D..dwaA6Qe/ipel/12D..bCcW8ab",
  "/p2p/12D..dJT6nXY/ipel/12D..bCcW8ab" // Follower
]
\end{lstlisting}
\end{minipage}
  \caption{The Log Multiaddress.}
  \label{ex:Multiaddress}
\end{example*}

@@

Much like IPFS Peers, Logs are identified on the network with addresses, or more specifically, with multiaddresses [ref]. Here we introduce IPEL, or Interplanetary Event Log, as a new protocol tag to be used when composing Log multiaddresses (see Example \ref{ex:Multiaddress}).

In practice, to reach a Log via it’s IPEL multiaddress, it must be encapsulated in an IPFS Peer multiaddress (see Example \ref{ex:Multiaddress}).

\begin{example}
\begin{lstlisting}
type AddrBook interface {
   AddAddr(thread.ID, peer.ID, ma.Multiaddr, time.Duration)
   AddAddrs(thread.ID, peer.ID, []ma.Multiaddr, time.Duration)
   SetAddr(thread.ID, peer.ID, ma.Multiaddr, time.Duration)
   SetAddrs(thread.ID, peer.ID, []ma.Multiaddr, time.Duration)
   UpdateAddrs(t thread.ID, id peer.ID, oldTTL time.Duration, newTTL time.Duration)
   Addrs(thread.ID, peer.ID) []ma.Multiaddr
   ClearAddrs(thread.ID, peer.ID)
}
\end{lstlisting}
\caption{AddrBook storing log addresses.}
\end{example} \label{ex:AddrBook}

@@

@@

\begin{example}
\begin{lstlisting}
// KeyBook stores log keys
type KeyBook interface {
   PubKey(thread.ID, peer.ID) ic.PubKey
   AddPubKey(thread.ID, peer.ID, ic.PubKey) error
   PrivKey(thread.ID, peer.ID) ic.PrivKey
   AddPrivKey(thread.ID, peer.ID, ic.PrivKey) error
   ReadKey(thread.ID, peer.ID) []byte
   AddReadKey(thread.ID, peer.ID, []byte) error
   FollowKey(thread.ID, peer.ID) []byte
   AddFollowKey(thread.ID, peer.ID, []byte) error
}
\end{lstlisting}
\caption{A KeyBook storing log keys.}
\end{example} \label{ex:KeyBook}

@@

Much like the Log address book, Log keys are stored in a key book (see Example \ref{ex:KeyBook}).

@@

\begin{example}
\begin{minipage}{.45\textwidth}
\begin{lstlisting}
type TextileKVStore interface {
  Put(key string, value interface{}) error
  Get(key string) (interface{}, error)
  Del(key string) error
}
\end{lstlisting}
\end{minipage}
\caption{The Key-Value store interface.}
\end{example} \label{ex:KVStore}

@@

\begin{example}
\begin{minipage}{.45\textwidth}
\begin{lstlisting}
type TextileDocumentStore interface {
  Put(doc Inedexable) error
  Get(key string) (Indexable, error)
  Del(key string) error
  Query(query Query) ([]Indexable, error)
}
\end{lstlisting}
\end{minipage}
\caption{The Document store interface.}
\end{example} \label{ex:AddrBook}

@@

\begin{example}
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=json,firstnumber=1]
{
  "_id": "bafykrq5i25vd64ghamtgus6lue74k", // TID
  "default": "no-access",
  "peers": {
    "12D..dwaA6Qe": ["write", "delete"],
    "12D..dJT6nXY": ["follow"],
    "12D..P2c6ifo": ["read"],
  }
}
\end{lstlisting}
\caption{blahblah}
\end{minipage}
\end{example}

@@

\begin{example}
\begin{lstlisting}[language=json,firstnumber=1]
{
  "_id": "bafykrq5i25vd64ghamtgus6lue74k-acl", // TID-acl
  "default": "no-access",
  "peers": {
    "12D..dwaA6Qe": ["write", "delete"],
  }
}
\end{lstlisting}
\caption{Blahblah}
\end{example}

@@

\begin{example*}

@@

\end{example*}
